\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Discussion: Synthesis and main contributions
Update on Overleaf.

>>>>

We ientified several limits to our model,
the major of which we will now detail. First,
the full framework is based on discrete time which
is incompatible with the analogous nature of biological
time. We have used the binning of time to ease
the implementation of the computational framework
on conventional hardware, especially GPUs,
and in particular by using the three-dimensional
convolution. We have tested the effect of this time
bin size and have shown it does not impact
the results shown here. This is consistent with the
relative robustness of other ff event-based
frameworks such as thots, where accuracy was
not changed when jittering input spikes by
up to 1ms noise (grimaldi zz]. This hints
at including analytically a precision term in
the temporal value of incoming spikes, a
mechanism potentially implemented by the
n 5 ms smoothing at the level of the PSC
of conventional synapses. Furthermore, it is
possible to overcome the problem using a purely
even d- based scheme. Indeed, it is not necessary to
compute voltage males between two spikes (Morrison)
and to define a purely event-driven framework.
A further limit is that the model that
we defined is purely feed-forward. It
results that the spikes generated by post-synaptic
neurons are produced solely based on the
information in the classical receptive field.
However, it is known that neurons in a
layer may interact using lateral interaction
[charane Lorry and that this may be the
basis of computational principles, for instance
of binding neighboring orientations (Bednar).
Moreover, neural information is modulated by
feedback information, for instance do distinguish
figure from background (Roefsema J and
has proven to be essential in building realistic
models of the primary visual areas (Boutin 2020
Boutin rozo feedback , Boutin '2oz]. It is nd
currently possible to implant these recurrent
connections (lateral or feedback), mainly because
of our use of convolutions. However the generic
model is capable of including this by
inserting spikes in the list of spikes reaching
the pipe-synaptic addresses. While possible
in theory, it should be properly adapted
in practice such that these recurrent
connections do not reach outside an
homeostatic state ( a death or a
blow-up of activity).
Suchreccarrentatvityweential
to implement predictive or anticipative
processes . This is essential in a neural
system as it contains multiple different
delays which necessitates a temporal
alignment (Hoogendoorn 2019]. This was
previously modeled to explain for instance
the flash - lag visual illusion (Khoei 2017)
As was previously started " ... " (reminet
20174], and our hetero-synaptic model
would provide with a simple and elegant
solution to that problem.
